landlord

### 2022-12-06 src/landlord.Rmd
don't make new sheet to write in

```{r}
#write result to google sheet
gs4_create("MSA_landlord_score")
sheet_write(MSA_landlord_data, ss = "https://docs.google.com/spreadsheets/d/1nLpDhM88a3rEBDVK5RZlk2B6QuwVIwvsfE5HeBz0mLo/edit?usp=sharing", sheet = "MSA_landlord_data")
```

>>>>

```{r}
#write result to google sheet
#gs4_create("MSA_landlord_score")
sheet_write(MSA_landlord_data, ss = "https://docs.google.com/spreadsheets/d/1nLpDhM88a3rEBDVK5RZlk2B6QuwVIwvsfE5HeBz0mLo/edit?usp=sharing", sheet = "MSA_landlord_data")
```
